The power of dark silicon

### 2018-01-03 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

>>>>

\hypertarget{requirements-elicitation-towards-the-unknown-unknowns}{%
\section{Requirements elicitation: Towards the Unknown
Unknowns}\label{requirements-elicitation-towards-the-unknown-unknowns}}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Abstract---Requirements elicitation research is reviewed using a
framework categorising the relative `knowness' of requirements
specification and Common Ground discourse theory. The main contribution
of this survey is to review requirements elicitation from the
perspective of this framework and propose a road map of research to
tackle outstanding elicitation problems involving tacit knowledge. The
paper concludes with remarks on the possibility of elicitation tackling
the most difficult question of `unknown unknown' requirements.

However, elicitation still remains problematic; missing or mistaken
requirements still delay projects and cause cost overruns in this paper
we set out to explore the field from the perspective made famous from
Donald Rumsfeld's quote of the ``known knowns, the known unknowns, and
unknown unknowns''. This perspective poses challenges to requirements
elicitation since it probes the boundaries of knowledge and who
possesses it, thereby creating a useful stress test for requirements
elicitation techniques, methods and tools.

Elicitation review framework (ERF). Tacit knowledge taxonomy based on
the properties of \emph{expressible} (know knowledge),
\emph{articulated} (documented domain knowledge), \emph{accesible} (need
memory recall), \emph{relevant} to the project: • Known knowns:
expressible, articulated, and relevant. • Known unknowns: not
expressible or articulated, but accessible and potentially relevant. •
Unknown knowns: potentially accessible but not articulated. • Unknown
unknowns: not expressible, articulated or accessible but still
potentially relevant.

From the perspective of the analyst/ stakeholder: - Known knowns: not a
problem - known unknowns: the analyst has a domain knowlegde but the
stakeholder may forgot or be unaware - Unknown knowns: the stakeholder
holds a knowlegde but it is not articulated, so the analyst has to
discover this tacit knowlegde and elicitate it. Once the stakeholder
shows a glimpse of his knowlegde the analyst realize that there is
something and the problem into known unknowns. - Unknown unknowns: the
analist and the stakeholder are unaware of what's missing, but it has
the potential to be relevant information.

The Tacit Knowledge Framework {[}14{]} poses three challenges: (i)
Identifying tacit knowledge: the unknown knowns; even when the analyst
suspects they exist (known unknowns), making tacit knowledge accessible
may not be easy. (ii) Knowing what is relevant and should be articulated
from the analyst's perspective: the necessary detail problem. (iii)
Articulating the knowledge where it is needed, in the correct context,
so it can be understood by all stakeholders.

The first step to solve the problem of unknown unknowns is to assume
that may exist a missing knowledge, and being prepared to invest in
order to find it. The goal is to convert the unknown unknowns into known
knowns.

Common ground theory explains how meaning is constructed by conversation
and action, which progresses towards a mutually agreed goal.

Action Ladder and Project: Meaning in conversations has different
layers: the surface of explicit expression, tacit knowlegde and
linguistic interpretation. Setting: where the conversation takes place
(time, location, domain knowledge) Arena: shared knowledge about the
culture, norms, history and assumptions which allow dialogue between
people to be interpreted in their context.

For our purposes, Common Ground contributes `tools for thought' which
can address the unknowns problems. For example the Arena suggests
questions to discover more detail of the users' background which may
uncover unknown concerns (viz cultural, political issues);

For many techniques the ability to detect the known unknowns depends on
the analyst's plan and the sampling strategy. In the case of interviews
the ability to dectect unknown unknowns depends on the follow-up
questions and sample size. Also interviews since they depends on natural
language communication there is always the possibility of ambiguous
interpretations.

Interviews approach natural human conversation so they support the
dynamic construction of understanding and exploration of the Arena and
Setting of the dialogue by explicit questions and observation. However,
interviews are weaker for reflection(reflection as an intentional,
active progression of learning), where the analyst has to rely on notes
and recordings. Furthermore, eliciting tacit knowledge depends on the
analysts' questioning skills interaction. Hence a combination of
techniques rather than structured interviews per se is probably the most
effective approach. .

There are four research directions to push the boundaries of the
unknown: Unknown knowns. The problem for the analyst is discovering what
the stakeholder knows but does not articulate. Sensitivity to political
issues, user values and emotions needs to be researched in depth to
provide `emotional intelligence' guidance for analysts so they can
anticipate these unknowns and elicit sensitive tacit knowledge. The
Common Ground quest is to be more sensitive to the stakeholder's
Setting, feelings, norms and culture

Known unknowns. In this case the analyst has some awareness of the
necessary knowledge, so an agenda for elicitation can be set. Most
techniques involve exploring the implications of the system-domain
boundary. Challenging assumptions, reasoning about the implications of
obstacles, and relaxing domain constraints need further research towards
not only hard influences, but also soft, probabilistic implications.

Design discovery. This is a variant of known unknowns where the
challenge is to solve the ``I'll know what I want when I see it''
problem. Much progress has been made in this area with prototypes,
storyboards and mock-ups; however, simulations and virtual worlds may
have further potential.

Unknown unknowns. Two approaches could address elicitation of
`over-the-horizon' knowledge. First, creative RE, which is already
established {[}55{]}, needs to be integrated with social media, so that
collaborative creative RE is empowered. This could involve designing
socio- technical elicitation systems, as e-communities, communities of
practice with global distributions for the increasing number of Internet
applications. Secondly, the use of analogies and examples, and also
counter examples, can challenge the boundaries of the possible to
develop new design ideas.

Known unknowns imply the need for exploration of the problem and
solution spaces; (e.g.) using a combination of obstacle anaylsis and
prototyping.
